---
title: "Testing the 'Other' category stuff"
output: html_notebook
---

The `place-apurp-cross.R` file was originally made to cross activity purpose and place to look at multitasking. However, it became the ground for fixing the issues within the place type. Once a final thin has been decided, these changes will be implemented into the script that is in the workflow called `01_02_classify-places-HWSO.R`

```{r}
library(here)
source(here("analysis","place-apurp-cross.R"))
```



```{r}
locs_rel_matched %>% group_by(place_type) %>% count() %>% View()
```


## Keeping track of the place counts in each round of "fixing" the other category:

1. After 
Home
219141
Other
230211
School
11885
Work
31084

2. After 
place_type      n
<chr>       <int>
1 Home       235333
2 Other      214735
3 School      11881
4 Work        30372


```{r}
#' Below: Number of places in each category and number of people with each of those place types

# pltype_frq <- locs_rel_matched %>% count(SAMPN,PERNO,place_type) %>%
#   group_by(place_type) %>% summarise(`Total Place-Events` = sum(n), `People with this place type` = n())
# 
# pltype_frq
# 
# pltype_frq %>% write_csv(here("figs", "place-type-freq-table-HOSW.csv"))
```

For each person, did they go to school/work on the diary day?

```{r}
locs_place_cat <- locs_rel_matched %>% 
  group_by(SAMPN,PLANO) %>%
  mutate(any_work   = any(place_type == 'Work'),
         any_school = any(place_type == 'School'),
         any_other  = any(place_type == 'Other')) %>% 
  ungroup() %>%
  select(SAMPN,PERNO,PLANO,place_type,any_work:any_other)
```

## Attaching place type to activity type
```{r}
activity <- chts_rel$ACTIVITY
ac <- activity %>% select(source, SAMPN, PERNO, PLANO, ACTNO, APURP) 


#get the new activity categories AND clean up category names
# activities_crosswalk <- readxl::read_excel(here("data", "activity_purps_crosswalk_touppercase.xlsx"))
# gather(key = "key", value = "old.apurp", -new.apurp, -Act_Cat) %>% 
# select(-key)



# act.cat <- ac %>% 
#   left_join(activities_crosswalk, by = c("APURP" = "old.apurp")) %>% 
#   mutate(APURP = new.apurp) %>% select(-new.apurp)


act.place <- ac %>% left_join(locs_place_cat, by = c("SAMPN", 'PERNO', 'PLANO'))

```



## place x activity


What activities are done in place type other?

```{r}
act.place %>% 
  filter(place_type == "Other") %>%
  # group_by(APURP, place_type) %>% 
  group_by(APURP) %>% 
  count %>% 
  # spread(place_type, n) %>% 
  # arrange(desc(n)) %>%
  # View()
  clipr::write_clip()
```


## What is still called Other?

```{r}
matching <- locs_rel_matched %>% 
  select(SAMPN, PERNO, PLANO,
         # LAT, LON, Home_Lat, Home_Lon, school_lat, school_lon, work_lat, work_lon, 
         home_match_loc, home_match_name, school_match_lat, school_match_lon, school_match_name1, school_match_name2, school_match_acts, work_match_lat, work_match_lon, work_match_name1, work_match_name2, work_match_acts,
         home_match_points, school_match_points, work_match_points,
         place_type, TRIPDUR, PNAME, school_name, work_name, work_name2)

matching %>% 
  filter(place_type == "Other") %>% 
  View()
```

```{r}
place <- chts_rel$PLACE

pl.name <- place %>% select(SAMPN, PERNO, PLANO, PNAME, LAT, LON)

act.pl.name <- act.place %>% left_join(pl.name)

act.pl.name %>% 
  filter(place_type == "Other") %>% 
  # filter(str_detect(APURP, "SCHOOL")) %>% 
  filter(str_detect(APURP, "IN SCHOOL/CLASSROOM/LABORATORY")) %>% 
  # select(place_type, APURP, PNAME) %>% 
  # group_by(APURP) %>%
  # count() %>%
  View()
```


Add the "matching" thing to it instead of place:
```{r}
act.match <- act.place %>% left_join(matching)
act.match %>% 
  filter(place_type == "Other") %>%
  # filter(place_type == "Home") %>% 
  # filter(str_detect(APURP, "IN SCHOOL/CLASSROOM/LABORATORY")) %>%
  # filter(str_detect(APURP, "ALL OTHER WORK-RELATED ACTIVITIES AT MY WORK")) %>%
  filter(str_detect(APURP, "ALL OTHER ACTIVITIES AT MY HOME")) %>%
  # group_by(PNAME) %>% 
  # count() %>% 
  # filter(PNAME == "HOME") %>%
  View
```


## FINDINGS ABOUT THE OTHER CATEGORY

* There are places where the name (WORK or SCHOOL) match, but the lat/lon don't
  + Sometimes because they did not put a lat/lon at all for their work, sometimes because they do not have a job that is in one place at a time (like landscaping)
* There are places where the lat/lon match, but the place name is not WORK or SCHOOL
* There are misspellings between work name and pname
* There are people who put DK/RF when reporting work name, but then put it in PNAME
* Some people put their titles in work_name instead of location of work (work_name = "Respiratory therapist", PNAME = "specific hospital")


# More exploring what's wrong with "Other" (i think)
(must run after `place-apurp-cross.R`)
```{r}
source(here("analysis","place-apurp-cross.R"))
```


```{r}
pl.small <- locs_rel_matched %>% 
  select(SAMPN, PERNO, PLANO, LAT, LON, Home_Lat, Home_Lon, MODE, PNAME, place_type, ACTDUR, TRIPDUR)


act.pl.oth <- act.cat %>% 
  left_join(pl.small, by = c("SAMPN", 'PERNO', 'PLANO'))%>% 
  # filter(place_type == "Home")
  filter(place_type == "Other")

act.pl.oth %>% 
  filter(APURP =="ALL OTHER ACTIVITIES AT MY HOME") %>% 
  # filter(is.na(PNAME)) %>% 
  mutate(lat.dif= (LAT - Home_Lat), lon.dif = (LON - Home_Lon)) %>% 
  # summarise_at(vars(lat.dif, lon.dif), list(~max(., na.rm = TRUE), ~min(., na.rm = TRUE)))
  View
  # clipr::write_clip()
```


```{r}
act.pl.oth %>% mutate(lat.dif= (LAT - Home_Lat), lon.dif = (LON - Home_Lon)) %>% 
  View
```


Findings so far:

* there are some places that people caled "home" that have a different lat/lon than the declared home lat/lon
* There are 

=======

## This is something else idk what
I think it's looking at issues with activity durations?
```{r}
act.pl.oth %>% 
  filter(ACTDUR == 1439) %>% 
  # filter(APURP == "LOOP TRIP (FOR INTERVIEWER ONLY-NOT LISTED ON DIARY)") %>% 
    View()
```


```{r}
act.pl.oth %>% mutate(lat.dif= (LAT - Home_Lat), lon.dif = (LON - Home_Lon)) %>% 
  View
```


Findings so far:

* there are some places that people caled "home" that have a different lat/lon than the declared home lat/lon
* There are 



### What are places that should be called "home" or "work" or "school" that are not being called that?



