---
title: "R Notebook"
output: html_notebook
editor_options: 
  chunk_output_type: console
---

FOR NOW: I will run an analysis excluding these people as an experiment to see how it goes. TOMORROW I will investigate who they are further




# investigate the NA's:

```{r message=FALSE, warning=FALSE}
library(tidyverse)
library(here)
```

```{r}
travel_dat <- read_rds(here("data", "places_travel-added.rds"))
```


## Look at who has the arrival and departure times as NA

Extract the pid's where any time value is NA
```{r}
pids_na_arr_dep <- travel_dat %>% 
  select(pid, arr_time3_add1, dep_time3_add1) %>%
  gather(key = "key", value = "value", -pid) %>% 
  filter(is.na(value)) %>% 
  .$pid %>% unique
```




Read the raw CHTS files, extract place file
```{r}
chts <- read_rds(here("data-raw", "chts_all_2019-05-22.rds"))
place <- chts$PLACE
```

Extract the rows with pids that have NA's for their arr/dep times
```{r}
library(magrittr)
place %<>% mutate(pid = str_c(SAMPN, PERNO, sep = "") %>% as.numeric())

pl_na <- place %>% filter(pid %in% pids_na_arr_dep)
```


Below, checking to see what arrival/departure times exist for PLANO == 1 in whole sample, and comparing to arr/dep times in `pl_na`

```{r}
pl1 <- place %>% filter(PLANO == 1) %>% select(source,pid, PLANO, ARR_HR, ARR_MIN, ARRTM)

pl1 %>%
  filter(!is.na(ARRTM)) %>% 
  .$ARRTM %>% 
  # unique %>% 
  View()

pl1 %>%
  filter(is.na(ARR_HR)) %>% 
  # .$ARRTM %>% 
  # unique %>% 
  View()

pl_na %>% filter(PLANO == 1) %>% 
  # select(pid, PLANO, ARR_HR, ARR_MIN, ARRTM) %>% 
  filter(!is.na(ARRTM)) %>% 
  .$ARRTM %>% 
  # unique %>% 
  View

```


All the people whose PLANO == 1, but arrival time is NOT NA are included in `pl_na`.

SRBI coded NA's for PLANO == 1, Nustats coded 3:00am for PLANO == 1. 

HOWEVER, Many of their PLANO == 1 have an ARRTM = NA. (correct formatting). So who are those people and why did they get NA's? I may need to move on to looking at the code itself for a bit. 


qUICK Question: how many people (unique pids) srbi vs nustats?
```{r}
per <- chts$PERSON
per %>% group_by(source) %>% count
```

There are 8080 in srbi, 109113 in nustats. And there are 8061 from srbi in the place file (the exact amount from srbi that are in the NA's)

How many of the na pids are from each?
```{r}
per %>% mutate(pid = str_c(SAMPN, PERNO)) %>% 
  filter(pid %in% pids_na_arr_dep) %>% 
  group_by(source) %>% count
```
ONLY 1 FROM NUSTATS, AND 8061 FROM SRBI.
WARNING: THIS MEANS I NEED TO LOOK AT THE START TIMES

who is the 1 from nustats:
```{r}
place %>%
  filter(pid %in% pids_na_arr_dep) %>% 
  filter(source == "NuStats") %>% View()
```


## Look at the code itself

### check modified place file
Compare `arrival_time_3` to `arr_time3_add1` (and the same for departure time)

Created in "02_modify-place-file.R"

```{r}
pl_mod <- read_rds(here("data","modified_pldat.rds"))
```

```{r}
pl_wat <- pl_mod %>% 
  select(pid, PLANO, arrival_time_3, arr_time3_add1, departure_time_3, dep_time3_add1) %>% 
  filter(is.na(arr_time3_add1))
```



### Check the creation of arrival_time_3

Apparently, the arrival/departure times should NOT be NA'S. They should be 0's. Going back to the creation of the arrival and departure times in this format. This is in the script `01_03_time-in-min-since-3am.R`

Below is the code from that script:
```{r}
convert_time_3A <- function(ext_time_col) {
  t3 = ext_time_col - 180
  if_else(t3 < 0, t3 + 24*60, t3)
}
```

```{r}
locations_timevars <- place %>% 
  mutate(arrival_time_3   = convert_time_3A(ARR_HR * 60 + ARR_MIN),
         departure_time_3 = convert_time_3A(DEP_HR * 60 + DEP_MIN),
         place_duration   = departure_time_3 - arrival_time_3 + 1,
         trip_duration    = TRIPDUR) # %>% select(SAMPN,PERNO,PLANO, arrival_time_3, departure_time_3, place_duration)
```

```{r}
x <- locations_timevars %>% select(pid,PLANO, ARR_HR, ARR_MIN, arrival_time_3, DEP_HR, DEP_MIN, departure_time_3, place_duration) %>% mutate(arrhr_min = ARR_HR *60)
```

### SRBI vs NUSTATS
what does srbi look like?
```{r}
srbi_place <- place %>% filter(source == "SRBI")
```

```{r}
activity <- chts$ACTIVITY
srbi_act <- activity %>% filter(source == "SRBI")
```

```{r}
srbi_arr_dep_times <- srbi_act %>% select(SAMPN, PERNO, PLANO, ARRTM, DEPTM) %>% distinct()
```


What I need to do: 
Get arrival/departure times from activity file from SRBI, divide by 60 to get the numbers we need, put that into the time-in-min-since-3am file. Could do an if/else statement.
```{r}
srbi_arr_dep_times <- srbi_act %>% 
  select(SAMPN, PERNO, PLANO, ARRTM, DEPTM) %>% 
  distinct() %>% 
  mutate(arr_hr = ARRTM%/%3600,
         arr_min = (ARRTM/60)%%60,
         dep_hr = DEPTM%/%3600,
         dep_min = (DEPTM/60)%%60)
```





# check for start/end time consistency

# make sure all start at time 1, end at time 1439 vs 1440

# NA'S in the middle?




# WHO is in `pl_na`

Here is what I have figured out:

* All the people whose PLANO == 1, but arrival time is NOT NA are included in `pl_na`.
* Apparently, the arrival/departure times should NOT be NA'S. They should be 0's.
* There are 8080 in srbi, 109113 in nustats. And there are 8061 from srbi in the place file (the exact amount from srbi that are in the NA's)

