---
title: "R Notebook"
output: html_notebook
---

This notebook will be the fresh examination ofthe investigation of arrival and departure times. I am doing this because the first one was getting long and difficult to navigate. This will be the continuation with the new file that uses the departure times that I discovered actually **were** present in the PLACE file. It was my mistake earlier because I did not notice that RStudio had changed the way they display tables in a way that hid the last 10 columns of the PLACE dataset.

```{r}
library(here);library(tidyverse)

# read in the modified place file
pl_mod <- readr::read_rds(here("data","modified_pldat.rds")) 
```

Object `pl_mod` made in `02_modify-place-file.R`. The version I am using right now was made on 2019-06-20

## Does this one have the same issues the other one had with arr/dep times?

Including: 
* departure times before arrival times
* DK/RF responses
* start and end times messed up

### Make sure all start at time 1, end at time 1439 vs 1440
```{r}

startendtimes <- pl_mod %>% # adds logical variables indicating the first and last places
  group_by(SAMPN, PERNO) %>% 
  mutate(firstplace = PLANO == min(PLANO),
         lastplace = PLANO == max(PLANO)) %>% 
  ungroup() %>% 
  select(source, pid, SAMPN, PERNO, PLANO, pltype, MODE, place_duration, arr_time3_add1, dep_time3_add1, firstplace, lastplace)

place1_timenot1 <- startendtimes %>% 
  # filter(PLANO == 1)
  filter(PLANO == 1 & arr_time3_add1 > 1) #extracts ppl who do not have 1 as their starting time on their first place

```
THERE ARE STILL 19 PEOPLE with place ==1 but start time is NOT 1. Missing time (all from srbi). 

Testing with place file pulled from a fresh download (re-ran all the other scripts to build the place file afterwards): STILL 19 people 

```{r}
pid_plano1_badarr <- place1_timenot1$pid %>% unique()
```


Are the last place times 1440?
```{r}
lastpl_timenot1440 <- startendtimes %>% filter(lastplace & dep_time3_add1 < 1438)
pid_plano1_baddep <- lastpl_timenot1440$pid %>% unique
```
WITH place file pulled from a fresh download, there are 88 people with (that is only 1 less than)

### check that arrival times come before departure times

```{r}
library(here);library(magrittr);library(tidyverse)
# chts <- read_rds(here("data-raw", "chts_all_2019-06-18.rds")) # new fixed up one!
# place <- chts$PLACE

# place %<>% mutate(pid = str_c(SAMPN, PERNO, sep = "") %>% as.numeric())
# travel_dat <- read_rds(here("data", "places_travel-added.rds"))
pl_mod <- read_rds(here("data","modified_pldat.rds")) 
```

```{r}
badsequences <- pl_mod %>% 
  mutate(duration = dep_time3_add1 - arr_time3_add1) %>% 
  select(source,pid, PLANO, arr_time3_add1, dep_time3_add1, duration, pltype, activity_type) %>% 
  filter(duration < 1) 

badseq_pid <-  badsequences %>%  .$pid %>% unique()

```
137 people now with bad sequences. THIS IS DOWN FROM 907 BEFORE SO USING THE ARR/DEP TIMES FROM PLACE FILE WORKED BETTER SO THAT'S GOOD.

```{r}
badguys <- pl_mod %>% 
  
  group_by(pid) %>% 
  mutate(lastplace = PLANO == max(PLANO)) %>% 
  ungroup() %>% 
  
  mutate(duration = dep_time3_add1 - arr_time3_add1,
         badseq = duration <1) %>% 
  filter(pid %in% badseq_pid) %>% 
  select(source,pid, PLANO, pltype, PNAME, arr_time3_add1, dep_time3_add1,duration, badseq,lastplace)
```


who are the people 
what are the srbi pltypes? correspondence between. 

```{r}
plsmall <- pl_mod %>% select(source, pid, PLANO, pltype, PTYPE, arr_time3_add1, dep_time3_add1)
srbipl <- plsmall %>% filter(source == "SRBI")
```


```{r}
summarytools::ctable(srbipl$pltype,srbipl$PTYPE,totals = TRUE)
```

ctab with the 900 ppl put back in to see what category (pltype) the missing times were put in

## dealing with  NA's

```{r}
library(here);library(magrittr);library(tidyverse)
# pl_mod <- read_rds(here("data","modified_pldat.rds")) 
```

CODE FROM `02_modify-place-file.R` to get the place file before we remove the NA's
```{r}
places_dat <- read_rds(here("data","places_county-selection.rds"))

### Recoding variables: Make personID variable, change starting times to 1 instead of 0 by adding one minute to everything, simpler place_types names, AND saving it as a data.frame so traminer can use it
#' I did this because traminer requires the sequence data to have no values <1
#' # Also Making the overall id variable, a shortened placetype variable, and recoding the already-included travel as "loop" and "transfer" since those were wrongly placed in the "Other" category.


pl_mod <- places_dat %>% 
  mutate(
    pid =            as.numeric(str_c(SAMPN, PERNO)),
    pltype =         recode(place_type, Other = "O", Home = "H", Work = "W", School = "S"), 
    arr_time3_add1 = arrival_time_3 + 1, 
    dep_time3_add1 = departure_time_3 + 1,
    activity_type =  if_else(condition = (purpose_A1 == "CHANGE TYPE OF TRANSPORTATION/TRANSFER (WALK TO BUS, WALK TO/FROM PARKED CAR)"),
                             true = "Transfer",
                             false = activity_type),
    activity_type =  if_else(condition = (purpose_A1 == "LOOP TRIP (FOR INTERVIEWER ONLY-NOT LISTED ON DIARY)"),
                             true = "Loop",
                             false = activity_type)) %>% 
  data.frame()
```


```{r}
na_pids <- pl_mod %>% 
  filter(is.na(arr_time3_add1) | is.na(dep_time3_add1)) %>% 
  .$pid %>% unique
  # filter(activity_type == "Transfer")

na_pl_records <- pl_mod %>% filter(pid %in% na_pids)

na_pl_records %>% select(pid, PLANO, MODE, place_type, arr_time3_add1, dep_time3_add1) %>% View()
```


```{r}

```


# NOTES

For the 19 ppl with start time bad we will impute Travel for the first thing of the day
for the 88 ppl with bad end times, 
if travel/transfer, put it in
if missing times, when activity type is "transfer" we call it Travel (?)
ppl who refused a lot - dump em


